Analysis plan

### 2023-09-07 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adjusting for new observation window and data

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Telecommuters" = "1",
                            "Office visitors" = "2",
                            "Hybrid workers" = "3",
                            "Disconnected workers" = "4",
                            "In-office workers" = "5"),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

@@

@@

```{r}
date_cohort_month_start <- ymd(params$date_cohort_month)
date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
date_observation_window_month_end <- 
  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
  date_observation_window_month_start %>% 
  rollbackward()
```

@@

```{r}
params$date_cohort_month %m+% months(params$observation_window_length_months)
```

Second, create a dataframe of all the days of the year.

```{r}
prep_b <- 
  tibble(
  date = seq.Date(from = ymd("2022-01-01"),
         to = ymd("2022-12-31"),
         by = "days")
)
```

@@

```{r}
prep_b %>% 
  skim()
```

@@

```{r}
ggsave(filename = fp, plot = p_2, width = 6, height = 3, units = "in")
```

>>>>

# Summary

@@

# CONTINUE FROM HERE

```{r}
beepr::beep(sound = 5)
```

```{r}

# Defining work pattern groups

```{r}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Telecommuters" = "1",
                            "Office visitors" = "2",
                            "In-office workers" = "3",
                            "Disconnected workers" = "4",
                            "Hybrid workers" = "5"),
    .cluster_5 = fct_relevel(.cluster_5,
                            "Telecommuters",
                            "Office visitors",
                            "Hybrid workers",
                            "In-office workers",
                            "Disconnected workers"
                            ),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

@@

```{r}
date_cohort_month_start <- ymd(params$date_cohort_month)
date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
date_observation_window_month_end <- 
  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
  date_observation_window_month_start %>% 
  rollbackward()
date_cohort_month_start
date_cohort_month_end
date_observation_window_month_start
date_observation_window_month_end
```

@@

Filter to just the days in the observation window.

```{r}
prep_b <- 
  prep_a %>% 
  filter(date >= date_cohort_month_start & date <= date_observation_window_month_end)

prep_b
```

Count the number of pay periods.

```{r}
prep_val_01 <- prep_b %>% 
  summarise(n_distinct(period_number)) %>% 
  pull()

prep_val_01
```

Calculate telework and onsite per pay period.

```{r}
d <- 
  d %>% 
  mutate(across(
    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
    .fns = ~./prep_val_01,
    .names = "{col}_ppp"
  ))
```

@@

```{r}
d %>% 
  skim(ends_with("_ppp"))
```

## Calculate averages

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(daily_status_reporting_to_job_site,
       daily_status_reporting_to_job_site_observation_prop,
       daily_status_reporting_to_job_site_working_prop,
       daily_status_reporting_to_job_site_ppp,
       daily_status_teleworking,
       daily_status_teleworking_observation_prop,
       daily_status_teleworking_working_prop,
       daily_status_teleworking_ppp,
       days_colocated_1,
       days_colocated_1_observation_prop,
       days_colocated_supervisor,
       days_colocated_supervisor_observation_prop,
       days_colocated_team,
       days_colocated_team_observation_prop,
       days_telework_team,
       days_telework_team_observation_prop,
       working_days,
       team_size_mode)
```

# Calculating ranges

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  summarise(
    across(
      .cols = c(daily_status_reporting_to_job_site_ppp,
                daily_status_reporting_to_job_site_working_prop,
                daily_status_teleworking_ppp,
                daily_status_teleworking_working_prop),
      .fns = list(q_025 = ~quantile(.,probs = .025),
                  q_975 = ~quantile(.,probs = .975))
    )
  ) %>% 
  pivot_longer(-.cluster_5) %>% 
  pivot_wider(values_from = value, names_from = .cluster_5)
```

# Regional difference.

```{r}
prep_d_01 <- 
  d %>% 
  group_by(location_state,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )# %>% 
  # mutate(
  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  # )

prep_d_03
```

# Office differences

```{r}
prep_d_01 <- 
  d %>% 
  group_by(gsa_sso) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_v_01 <- 
  prep_d_01 %>% 
  slice(2) %>% 
  pull(n)

prep_d_02 <-
  d %>%
  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
         gsa_sso = fct_infreq(gsa_sso)) %>%
  group_by(gsa_sso,.cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>% 
  rename(num = n) %>% 
  mutate(gsa_sso = fct_relevel(gsa_sso,
                               "PBS",
                               "FAS",
                               "OCFO",
                               "Other"))

prep_d_03 <- 
  prep_d_02 %>% 
  filter(gsa_sso != "Other")

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )

prep_d_05 %>% view()
```

@@

```{r}
ggsave(filename = fp, plot = p_2, width = 6, height = 3, units = "in")
```
# Clusters: How much telework?

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = mean(daily_status_teleworking)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(y = max(density(daily_status_teleworking)$y),
            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
  )
```

```{r}
p_1 <- 
  prep_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = num, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean days of telework") +
  theme_light() +
  oescolorrrs::scale_fill_oes() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_2 <- 
  d %>% 
  ggplot(
    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
  ) +
  geom_density(alpha = .5) +
  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
  xlab("Days of telework") +
  ylab("Density") +
  theme_light() +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme(legend.position = "None")

p_1|p_2
```

# Clusters: How much telework? (proportion of working)

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = mean(daily_status_teleworking_working_prop)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(y = max(density(daily_status_teleworking_working_prop)$y),
            x = density(daily_status_teleworking_working_prop)$x[density(daily_status_teleworking_working_prop)$y == max(density(daily_status_teleworking_working_prop)$y)]
  )
```

```{r}
p_1 <- 
  prep_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = num, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean days of telework") +
  theme_light() +
  oescolorrrs::scale_fill_oes() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_2 <- 
  d %>% 
  ggplot(
    aes(x = daily_status_teleworking_working_prop, color = .cluster_5, fill = .cluster_5)
  ) +
  geom_density(alpha = .5) +
  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
  xlab("Days of telework") +
  ylab("Density") +
  theme_light() +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme(legend.position = "None")

p_1|p_2
```
